
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{todonotes}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\sitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingg}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newenvironment{subheadingListing}{\begin{itemize}[leftmargin=*]}{\end{itemize}}
\newenvironment{resumeList}{\begin{itemize}}{\end{itemize}\vspace{-5pt}}

  \newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Stepan Klos}} & Email: \href{mailto:stepanklos@gmail.com}{stepanklos@gmail.com}\\
  %\href{https://blog.stkl.cz}{blog.stkl.cz}\\%
  \href{https://www.linkedin.com/in/stepanklos}{\textbar\enspace linkedin.com/in/stepanklos}
  & Location: Prague, Czech Republic \\
  %\href{www.linkedin.com/in/stepanklos}{www.linkedin.com/in/stepanklos} |%
  \href{https://github.com/KlosStepan}{\textbar\enspace github.com/KlosStepan}\\
  \href{https://blog.stkl.cz}{\textbar\enspace blog.stkl.cz}
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Professional Experience}
\begin{subheadingListing}
  \resumeSubheading
  {MSD (Merck Sharp \& Dohme LLC)}{Next.js, Python, Kubernetes}
  { Technical Lead + Senior JavaScript Engineer}{Nov 2024 – now}
  \begin{resumeList}
    \sitem{Led transfer of a GenAI solution from vendor to MSD, ensuring compliance and enterprise integration.}
    \sitem{Built and led an engineering team to deploy on AWS K8s, add features, and optimize performance.}
    \sitem{Delivered a scalable, secure GenAI tool central to Merck’s AI transformation and FDA-facing operations.}
    \sitem{Aligned technical delivery with business and regulatory goals through cross-functional collaboration.}
  \end{resumeList}

  \resumeSubheading
  {Prague Institute of Planning and Development}{ES6 (React 18, Node.js), Docker and Kubernetes}
  {Full Stack Engineer \& DevOps Engineer}{February 2022 – February 2024}
  \begin{resumeList}
    \sitem{Developed two React/Node web applications for streamlining city planning processes in Prague.}
    %\sitem{Working on Dockerization - exploring the best self-hosted cloud solution, be it OpenShift/VMware Tanzu/plain Kubernetes. Helping other developers to migrate their applications to run in Kubernetes.}
    \sitem{Managed deployment of flagship Geoportal application to Azure AKS. Conducted evaluation of cloud platforms; managed AWS/DOKS and self-hosted K8s/OpenShift/Tanzu environments before migration.}
  \end{resumeList}

  \resumeSubheading
    {Office of the Government of the Czech Republic}{React 17, PHP, Python}
    {Full Stack Engineer}{Feb 2020 – Jul 2021}
    \begin{resumeList}
      \sitem{Built a React app with PHP API and Python data pipeline to publish national science results efficiently.}
      \sitem{Supported distribution of approx. half of Czech science funding - 1.77\% of GDP via the M17+ method.}
    \end{resumeList}

\resumeSubheading
{SwimmPair for TJ Prostejov}{Vanilla JavaScript, PHP}
{Fullstack Software Project – Contract}{Oct 2018 – Nov 2019}
\begin{resumeList}
  \sitem{Developed web app for managing swimming competitions with custom drag\&drop UI (DOM API), AJAX interactions, and responsive design for mobile and print.}
  \sitem{Designed PHP backend with object classes and approx. 80 API endpoints using stored procedures (loops, locks, checksums) to read/write data.}
\end{resumeList}


  \resumeSubheading
  {ELAI Prague}{Wordpress, PHP, CSS}
  {Web Developer}{February 2016 – December 2016}
  \begin{resumeList}
\sitem{Innovation Week 2016 \& Global Entrepreneurship Week Prague 2016 – Wordpress websites with plugins.}
 \end{resumeList}

  \resumeSubheading
  {Freelance}{Wordpress, PHP, JavaScript, CSS}
  {Websites for various customers and NGOs (10+)}{since 2010}
  \begin{resumeList}
    \sitem{jaromirstetina.cz (2015) - Member of European Parliament; social media integration.}
    %\sitem{c-d-s.cz (2013) and heart-of-europe.org (2014) - Czech Debate Organization tournaments operations; Heart of Europe Debate Tournament 40+ international teams registrations/payments/calendar \& stuff. }
    %\sitem{autoservispolena.cz (2017) - Car repair and maintenance business; contracted with graphic professional.}  
    \sitem{other – \textasciitilde 10 smaller websites with custom PHP backends, HTML/CSS, and interactive JS features.}

  \end{resumeList}

\end{subheadingListing}


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
\begin{subheadingListing}
  \sitem{
    \textbf{Programming Languages}{: ECMAScript 6, Go, Python, \CC, C\#, Java, Bash}
  }
  \sitem{
    \textbf{Frontend}{: React (Redux, Router), HTML5/CSS3, DOM API, Bootstrap, C++/Qt, C\#/Xamarin (XAML)}
  }
  \sitem{
    \textbf{Backend}{: Node.js, Go, MongoDB, Docker, Kubernetes, WebAssembly, Linux, Firebase, PHP, SQL, .NET}
  }
\end{subheadingListing}


%-----------EDUCATION-----------------
\section{Education}
\begin{subheadingListing}

  \resumeSubheadingg
  {Bachelor's Degree in CS (dropout)}{Charles University – Prague, Czech Republic}

  \begin{resumeList}
  \sitem{Completed approximately 80\% of coursework in mathematics and computer science.}
    %\sitem{Ran popular meme page “Matfyz memes that will make you CVUT” with 5000+ likes.}
    \sitem{Thesis: SwimmPair --- Code: \href{https://github.com/KlosStepan/SwimmPair-Www}{SwimmPair-Www}; thesis: \href{https://github.com/KlosStepan/SwimmPair-Thesis-TeXFiles}{SwimmPair-Thesis-TeXFiles} (export thesis.pdf).}
  \end{resumeList}
\end{subheadingListing}

%-----------PROJECTS-----------------
%-----------PROJECTS-----------------
\section{Personal Projects}
\begin{subheadingListing}

\resumeSubheadingg
{\href{https://lightningeverywhere.com/}{LightningEverywhere.com}}{React.js, Go, MongoDB, Docker}
\begin{resumeList}
  \sitem{Collecting places accepting Lightning Network (Bitcoin L2) worldwide. See: \href{https://lightningeverywhere.com/}{project}, \href{https://github.com/KlosStepan/Lightning-map}{code}, \href{https://blog.stkl.cz/10-prototype-lightning-project/}{blogpost}.}
\end{resumeList}


\end{subheadingListing}


%\end{subheadingListing}
%-------------------------------------------
\end{document}
